Comparative Analysis of Legislative Complex Networks of Select North American and European Countries

### 2018-12-11 paper/paper.tex
adding potential results

\begin{abstract}
    Given the complex nature of today's political climate, we were interested in analyzing and quantifying various legislative bodies in select first-world countries. To do so, we performed complex network analysis on seven North Amerian and European countries (Austria, Denmark, France, Sweden, Switerland, UK, and US) to understand how a wide variety political parties interacted amongst each other with respect to cosponshorship. We found and plotted summary statistics and centrality measures to make comparisons possible.
    % To-do: Finish abstract %
\end{abstract}

@@

\section{Results}

>>>>

\begin{abstract}
    Given the complex nature of today's political climate, we were interested in analyzing and quantifying various legislative bodies in select first-world countries. To do so, we performed complex network analysis on seven North Amerian and European countries (Austria, Denmark, France, Sweden, Switerland, UK, and US) to understand how a wide variety political parties interacted amongst each other with respect to cosponshorship. We found and plotted summary statistics and centrality measures to make comparisons possible.
\end{abstract}

@@

\section{Results}
\begin{itemize}
  \item Comparison of Number of Edges and Number of Vertices: UK has the largest number of vertices but one of the smallest number of edges (large number of people but very few connections made between them in comparison to other countries)
  \item Average Degree: US has average degree which is much higher than the average degree for other countries (each node is very highly connected to many other nodes)
  \item Comparison of Number of Edges and Average Distance: US has a much larger average number of edges when compared to other countries but has the second smallest average distance (there are many nodes but they are very highly connected so the distance between any two random nodes is much less than other countries)
  \item Comparison of Size of LCC and Number of CC: US has the largest average size of LCC but has the smallest number of CC (US are very highly connected and only has a few connected components)
\end{itemize}
